Pool Model

### 2025-08-28 pool_model.tex
make caption nicer
comment out fiture; no need

    \includegraphics[width=0.6\textwidth]{Figures/interaciton_potential.png}
        Overall form of the interaction force between two cells.
        A value $\sigma<1$ indicates that cells are overlapping which results in a positive force outwards.
        Conversely, as long as cells are apart $\sigma>=1$, no force is acting.
    \label{fig:spatial-interaction-potential}

@@

        List paramters for both models.
        To view, how these parameters are stored inside a cell-agent, we refer to the supplementary material~\ref{sec:supplement-full-parameters}.

>>>>

% \begin{figure}
%     \centering
%     \includegraphics[width=0.6\textwidth]{Figures/interaciton_potential.png}
%     \caption{
%         Overall form of the interaction force between two cells.
%         A value $\sigma<1$ indicates that cells are overlapping which results in a positive force outwards.
%         Conversely, as long as cells are apart $\sigma>=1$, no force is acting.
%     }
%     \label{fig:spatial-interaction-potential}
% \end{figure}

@@

        Comparison of the parameters for the \ac{ode} model and \ac{abm}.
        To view, how these parameters are stored inside a cell-agent, we refer to the supplementary
        material~\ref{sec:supplement-full-parameters}.
